Competing Bandits: The Perils of Exploration under Competition

### 2018-09-05 paper/content/introduction.tex

Multi-armed bandits (MAB) is a tractable abstraction for the tradeoff between exploration and \emph{exploitation} (making good near-term decisions based on available information). MAB problems have been studied for many decades, see \cite{Bubeck-survey12} for background. We consider i.i.d. rewards, a well-studied and well-understood MAB model \cite{bandits-ucb1}. We focus on a well-known distinction between ``greedy" (exploitation-only) algorithms, ``naive" algorithms that separate exploration and exploitation, and ``smart" algorithms that combine them. \asedit{Switching from ``greedy" to ``naive" to ``smart" comes with substantial adoption costs in infrastructure and personnel training \cite{MWT-WhitePaper-2016,DS-arxiv}.}

>>>>

Multi-armed bandits (MAB) is a tractable abstraction for the tradeoff between exploration and \emph{exploitation} (making good near-term decisions based on available information). MAB problems have been studied for many decades, see \cite{Bubeck-survey12} for background. We consider i.i.d. rewards, a well-studied and well-understood MAB model \cite{bandits-ucb1}. We focus on a well-known distinction between ``greedy" (exploitation-only) algorithms, ``naive" algorithms that separate exploration and exploitation, and ``smart" algorithms that combine them. Switching from ``greedy" to ``naive" to ``smart" algorithms involves substantial adoption costs in infrastructure and personnel training \cite{MWT-WhitePaper-2016,DS-arxiv}.
